Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2025-12-22 revision_whittaker.tex
Adds a remark on Shelstad's terminology and another on fundamental series

Recall that the \emph{Weyl chambers} of~$\mathfrak{t}^\ast$ are the connected components of the set of regular elements. Each Weyl chamber specifies a positive root system for the roots of $\mathfrak{t}$ in~$\g$, and we say a Weyl chamber is \emph{large} if the corresponding simple roots are all noncompact.

If~$\lambda \in \mathfrak{t}^\ast$ is a representative for the Harish-Chandra parameter of a discrete series representation $\pi$, then~$\pi$ is generic if and only if the Weyl chamber containing~$\lambda$ is large. See~\cite[Section 6]{vogan-gelfand-kirillov}.

@@

\begin{remarkplain} \textcolor{red}{\textup{TODO : add a remark about the case of fundamental series packets, in case there is no DS. }}\end{remarkplain}

>>>>

Recall that the \emph{Weyl chambers} of~$\mathfrak{t}^\ast$ are the connected components of the set of regular elements. Each Weyl chamber specifies a positive root system for the roots of $\mathfrak{t}$ in~$\g$, \textcolor{red}{[new]} and a Borel subgroup of~$G$ containing~$T$ and defined over~$\R$ \textcolor{red}{[/new]}. We say a Weyl chamber is \emph{large} if the corresponding simple roots are all noncompact.

If~$\lambda \in \mathfrak{t}^\ast$ is a representative for the Harish-Chandra parameter of a discrete series representation $\pi$, then~$\pi$ is generic if and only if the Weyl chamber containing~$\lambda$ is large. See~\cite[Section 6]{vogan-gelfand-kirillov}. \textcolor{red}{[new]} In the terminology of Shelstad~\cite[Section 2.3]{shelstad}, if $B$~is the corresponding Borel subgroup of~$G$, then $(B, T)$ is a fundamental Borel pair of Whittaker type.\textcolor{red}{[/new]}

@@

\begin{remarkplain} 
 \textcolor{red}{[NEW]} Not all quasi-split real groups have discrete series representations. But if $G(\R)$ is a quasi-split real group, then the  \emph{fundamental series} representations that are generic are irreducibly induced from generic discrete series of a maximal cuspidal Levi subgroup $M(\R)$ of $G(\R)$. Using \cite[Chapter~14]{abv}, especially Lemma 14.11 there, one may relate Whittaker data for $G(\R)$ with Whittaker data for $M(\R)$, and the generic fundamental series representations in a given $L$-packet for $G(\R)$ (together with the attached Whittaker data) with  generic discrete series representations for maximal cuspidal Levi subgroups. We shall not pursue this here. \textcolor{red}{[/NEW]}
 \end{remarkplain}
